### 2020-01-06 README.Rmd
update-documentation

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/gosset)](https://cran.r-project.org/package=gosset)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/agrobioinfoservices/gosset?branch=master&svg=true)](https://ci.appveyor.com/project/kauedesousa/gosset)
[![Build Status](https://travis-ci.org/agrobioinfoservices/gosset.svg?branch=master)](https://travis-ci.org/agrobioinfoservices/gosset)
[![codecov](https://codecov.io/gh/agrobioinfoservices/gosset/master.svg)](https://codecov.io/github/agrobioinfoservices/gosset?branch=master)
[![GPLv3 license](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.r-project.org/Licenses/GPL-3)
<!-- badges: end -->

@@

    library("devtools")
    devtools::install_github("agrobioinfoservices/gosset", upgrade = "never")

@@

The full functionality of **gosset** is illustrated in the package vignette. The vignette can be found on the [package website](https://agrobioinfoservices.github.io/gosset/).

## Contribution

You are welcome to contribute to this project. Please read our [contribution guideline](CONTRIBUTING.md).

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/gosset)](https://cran.r-project.org/package=gosset)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/agrobioinfoservices/gosset?branch=master&svg=true)](https://ci.appveyor.com/project/kauedesousa/gosset)
[![Build Status](https://travis-ci.org/agrobioinfoservices/gosset.svg?branch=master)](https://travis-ci.org/agrobioinfoservices/gosset)
[![codecov](https://codecov.io/gh/agrobioinfoservices/gosset/master.svg)](https://codecov.io/github/agrobioinfoservices/gosset?branch=master)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![GPLv3 license](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.r-project.org/Licenses/GPL-3)
<!-- badges: end -->

@@

```r

library("devtools")
devtools::install_github("agrobioinfoservices/gosset", build_vignettes = TRUE)

```

## Example

@@

The full functionality of **gosset** is illustrated in the package vignette. The vignette can be found on the [package website](https://agrobioinfoservices.github.io/gosset/) or from within `R` once the package has been installed, e.g. via

```r

vignette("Overview", package = "gosset")

```

## Meta

* Please [report any issues or bugs](https://github.com/agrobioinfoservices/gosset/issues).

* License: GPL-3

* Get citation information for *gosset* in R by typing
`citation(package = "gosset")`.

* You are welcome to contribute to the *gosset* project. Please read our [contribution guide lines](CONTRIBUTING.md).

* Please note that the *gosset* project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in the *gosset* project you agree to abide by its terms.
